\documentclass[a4paper,11pt]{article}
\usepackage[margin=1in,top=0.5in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{automata,positioning,arrows.meta}
\usepackage{enumitem}

% Formatting settings
\setlength{\parindent}{0pt}
\setlist[enumerate]{itemsep=0.3em, topsep=0.5em}

\newcommand{\vsp}{\vspace{0.5em}}
\newcommand{\bsp}{\vspace{1em}}
\newcommand{\ruler}{
    \vspace{1em}
    \hrule
    \vspace{1em}
}
\newcommand{\bsq}{\hfill $\blacksquare$}

\begin{document}

{\Large \textbf{ICMA 346 Project Report: The Tennessee Pterodactyls}}\\
{\normalsize Artem Kiselev, 6580846}

\section*{Problem Requierments and Formulation}
We have a yearly budget of \$50~million to sign free agents from the following table:

\begin{table}[htbp]
\centering
\renewcommand{\arraystretch}{1}
\begin{tabular}{rlcccccc}
\hline
& \textbf{Player} & \textbf{Position} & \textbf{Points} & \textbf{Rebounds} & \textbf{Assists} & \textbf{Minutes} & \textbf{Salary (\$M)} \\
\hline
1  & Mack Madonna        & Back court  & 14.7 & 4.4  & 9.3 & 40.3 & 8.2  \\
2  & Darrell Boards      & Front court & 12.6 & 10.6 & 2.1 & 34.5 & 6.5  \\
3  & Silk Curry          & Back court  & 13.5 & 8.7  & 1.7 & 29.3 & 5.2  \\
4  & Ramon Dion          & Back court  & 27.1 & 7.1  & 4.5 & 42.5 & 16.4 \\
5  & Joe Eastcoast       & Back court  & 18.1 & 7.5  & 5.1 & 41.0 & 14.3 \\
6  & Abdul Famous        & Front court & 22.8 & 9.5  & 2.4 & 38.5 & 23.5 \\
7  & Hiram Grant         & Front court & 9.3  & 12.2 & 3.5 & 31.5 & 4.7  \\
8  & Antoine Roadman     & Front court & 10.2 & 12.6 & 1.8 & 44.4 & 7.1  \\
9  & Fred Westcoast      & Front court & 16.9 & 2.5  & 11.4 & 42.7 & 15.8 \\
10 & Magic Jordan        & Back court  & 28.5 & 6.5  & 1.3 & 38.1 & 26.4 \\
11 & Barry Bird          & Front court & 24.8 & 8.6  & 6.9 & 42.6 & 19.5 \\
12 & Grant Hall          & Front court & 11.3 & 12.5 & 3.2 & 39.5 & 8.6  \\
\hline
\end{tabular}
\end{table}

\vspace{-0.5em}
The requirements are:
\begin{enumerate}
  \item Sign exactly 5 players.
  \item Total points per game $\ge80$.
  \item Total rebounds per game $\ge40$.
  \item Total assists per game $\ge25$.
  \item Total minutes per game $\ge190$.
  \item At most 2 front court and at most 3 back court players. As we must sign 5 players, we can simplify this to just require exactly 2 front court players.
  \item Select the group that satisfies requirements 1-6 at minimum total salary cost.
\end{enumerate}

Define a vector $\bm{x} \in \{0, 1\}^{12}$, consisting of the following binary decision variables:
$$x_i=\begin{cases}1,&\text{if player }i\text{ is signed,}\\0,&\text{otherwise,}\end{cases}\quad i=1,\dots,12.$$ 
Let
$\bm{s},\bm{p},\bm{r},\bm{a},\bm{m}\in\mathbb{R}_{+}^{12}$ be the salary, points, rebounds, assists, minutes vectors, and
$\bm{f}\in\{0,1\}^{12}$ indicate front court (1) or back court (0).

\vspace{1em}
We can now formulate the integer linear programming model:
\[
\begin{aligned}
\text{minimize} \quad & z=\bm{s}^\top\bm{x}\\
\text{subject to}\quad
&\bm{1}^\top\bm{x}=5,\\
&\bm{p}^\top\bm{x}\ge80,\\
&\bm{r}^\top\bm{x}\ge40,\\
&\bm{a}^\top\bm{x}\ge25,\\
&\bm{m}^\top\bm{x}\ge190,\\
&\bm{f}^\top\bm{x}=2, \\
&\bm{x}, \bm{f} \in \{0,1\}^{12}, \\
&\bm{s}, \bm{p}, \bm{r}, \bm{a}, \bm{m} \in \mathbb{R}_+^{12}.
\end{aligned}
\]

\section*{Linear Programming Solution}

\textbf{Question A.} 
Formulate an integer linear programming model (ILP) to help the general manager and coach determine which players they should sign and solve it by using the computer.

\ruler

\textbf{Ans A.}

\ruler

\vsp

\textbf{Question B.} 
Is the money provided by the owner sufficient to sign the group of players identified in (A)? If not, reformulate the model so that the available funds are a constratint and the objective is to maximize the average points of the group.

\ruler

\textbf{Ans B.}

\section*{Answers to Case Questions}

\section*{Sensitivity Analysis}

\section*{Insights from Sensitivity Analysis}

\end{document}